### 2024-07-12 machine-learning.qmd
Built site for gh-pages
20240627 - sessionInfo() for reproducibility
20240627 - sessionInfo()
20240703 - conclusion section

# Data Visualization {#sec-dataVisualization}

## Getting Started

### Load Packages

@@

>>>>

# Machine Learning {#sec-machineLearning}

## Getting Started {#sec-machineLearningGettingStarted}

### Load Packages {#sec-machineLearningLoadPackages}

@@

## Fitting the Traditional Regression Models {#sec-fittingModels-regression}

### Regression with One Predictor {#sec-regressionOnePredictor}

### Regression with Multiple Predictors {#sec-regressionMultiplePredictors}

## Fitting the Machine Learning Models {#sec-fittingModels-machineLearning}

### Least Absolute Shrinkage and Selection Option (LASSO) {#sec-lasso}

### Ridge Regression {#sec-ridgeRegression}

### Elastic Net {#sec-elasticNet}

### Random Forest Machine Learning {#sec-randomForest}

### *k*-Fold Cross-Validation {#sec-kfoldCV}

### Leave-One-Out (LOO) Cross-Validation {#sec-looCV}

## Conclusion {#sec-machineLearningConclusion}

::: {.content-visible when-format="html"}

## Session Info {#sec-machineLearningSessionInfo}

```{r}
sessionInfo()
```

:::
